%-------------------------
% Rover Resume - Star Template
% Link: https://github.com/subidit/rover-resume
%
% CUSTOM COMMANDS \aux{} and \rside{} for part formatting
% eg. \subsection{Company Name \aux{Designation} \rside{Duration}}
% Double lined titles with \subsection{} and \subsubsection{}
% \linkicon gives external link icon
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[sfdefault,semibold,lf]{FiraSans}
% \usepackage[a4paper,margin=0.4in]{geometry} % reduced bottom margin from 1in to 0.5in
\usepackage[letterpaper,margin=0.5in]{geometry} % Document margins

\usepackage{xcolor}
\definecolor{accent}{HTML}{141E61}

\setcounter{secnumdepth}{0}
\pdfgentounicode=1

%====== LIST FORMATTING ======
\usepackage{enumitem}
\setlist[itemize]{nosep, left=0pt .. 1.5em}
\setlist[enumerate]{left=0pt..1.5em}
\setlist[description]{itemsep=0pt}

%====== TITLE FORMATTING ======
\usepackage{xhfill}
\usepackage{soul}
\newcommand{\midrule}[1]{
  \leavevmode
  \xrfill[.5ex]{1pt}[accent]~\so{#1}~\xrfill[.5ex]{1pt}[accent]
}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{*2}{*1}
\titlespacing{\subsection}{0pt}{*3}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{\midrule}
\titleformat*{\subsection}{\large\bfseries}

%====== CUSTOM COMMANDS ======
\newcommand{\aux}[1]{
  $|$ \space {\small\normalfont\itshape #1}%
}

\newcommand{\rside}[1]{
  \hfill {\small\color{accent} #1}%
}

% \setlength{\headheight}{-0.5in}
% \setlength{\topmargin}{-0.5in}

%====== FOOTER ======
% \usepackage{lastpage}
% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhf{}
% \renewcommand{\headrulewidth}{0pt}

% Replace 'Star Rover' with your name in next line
% \fancyfoot[C]{\small\color{gray} Star Rover -- Page \thepage\ of \pageref*{LastPage}}

\pagestyle{empty}
% uncomment previous line to hide page numbering

%====== PACKAGES ======
\usepackage{fontawesome5}
% \usepackage{multicol}
\usepackage[bookmarks=false,hidelinks]{hyperref}
% Typography & justification enhancements
\usepackage{microtype}
\usepackage{ragged2e}
\Urlmuskip=0mu plus 1mu
\tolerance=1000
\pretolerance=500
\emergencystretch=2em

%====== FINISH PREAMBLE ======

%====== DOCUMENT STARTS HERE ======

\begin{document}
\justifying

%====== BANNER ======

\begin{center}
  {
    \fontsize{26}{12}
    \fontseries{heavy}\selectfont
    \color{accent}
    Ayush Jaipuriyar
  } \\ \medskip

  % {\color{gray}{\faHome}} 1 infinite loop, CA \hspace{0.1em}

  {{\color{gray}\faGlobe}: Glasgow, UK}
  \href{tel:+4407721170466}{\faPhone\: +4407721170466} \hspace{0.1em}
  \href{mailto:ayushjaipuriyar21@gmail.com}{\faEnvelope\: ayushjaipuriyar21@gmail.com} \hspace{0.1em}
  \href{https://github.com/ayushjaipuriyar}{\faGithub\: ayushjaipuriyar} \hspace{0.1em}
  \href{https://www.linkedin.com/in/ayushjaipuriyar}{\faLinkedin\: ayushjaipuriyar}
\end{center}
%==========
% \section{Summary}
%==========
% Backend-focused software engineer with hands-on experience delivering production-ready services on AWS. Shipped CI/CD, observability, and security controls; collaborate with cross-functional teams to drive measurable performance and reliability gains. Strengths include microservices architecture, REST/WebSocket APIs, caching/search (Redis, Elasticsearch), and automation.
%==========
\section{Education}
%==========
\subsection{University of Glasgow \aux{MSc in Computer Science} \rside{Sep. 2024 -- Sep. 2025}}
\subsection{Manipal University Jaipur \aux{BTech in Information Technology} \rside{Jun. 2020 -- Jun. 2024}}

%====== BANNER END ======
\section{Experience}
%===================

\subsection{Healthtrip \rside{Noida, India}}
\subsubsection{Software Developer Intern \rside{Jan. 2024 -- Aug. 2024}}
\begin{itemize}
  \item Spearheaded migration of 50\% of a PHP monolith to \textbf{NestJS}, improving scalability and performance by \textbf{~75\%} for \textbf{10K+ daily users}.
  \item Overhauled content delivery with \textbf{Redis caching} and \textbf{Elasticsearch indexing}, cutting data retrieval time by \textbf{~90\%} and boosting search performance by \textbf{~60\%}.
  \item Shipped an in-house \textbf{translation-management web app} supporting \textbf{9 languages}, replacing a brittle third-party crawler and increasing engagement by \textbf{~75\%}.
  \item Engineered production-ready \textbf{REST + WebSocket APIs} with \textbf{RBAC policies}, improving interoperability, scalability, and system security by \textbf{40--60\%}.
  \item Managed \textbf{AWS + Cloudflare infrastructure} (EC2, S3, CloudFront, SSL, WAF, caching), enhancing security and cutting global page load times by \textbf{~50\%}.
  \item Established \textbf{CI/CD pipelines} (GitHub Actions to AWS EC2) for automated beta/stable rollouts, reducing deployment time from hours to minutes.
  \item Conducted \textbf{unit and integration testing} using Postman and Jest, ensuring reliability and high code quality across services.
  \item Collaborated with cross-functional \textbf{frontend (Next.js)}, \textbf{Android}, and \textbf{Python} teams to debug APIs and streamline delivery pipelines, accelerating feature releases by \textbf{~30\%}.
\end{itemize}

\subsection{AST Consulting \rside{New Delhi, India}}
\subsubsection{Software Developer Intern \rside{Jun. 2023 -- Aug. 2023}}
\begin{itemize}
  \item Architected and maintained backend services using \textbf{NestJS}, \textbf{MongoDB}, and \textbf{TypeScript}, improving maintainability and modularity.
  \item Built and deployed a \textbf{CDN on AWS} (\textbf{S3}, \textbf{CloudFront}, \textbf{EC2}), cutting image load times by \textbf{~50\%} and reducing latency by \textbf{~40\%}.
  \item Set up \textbf{CI/CD pipelines} with \textbf{GitHub Actions} and \textbf{Docker}, accelerating deployments by \textbf{~40\%} and ensuring \textbf{95\%+ uptime}.
  \item Introduced structured \textbf{code review} and \textbf{version control workflows} via GitHub, reducing post-release bugs by \textbf{~30\%}.
  \item Automated key operations with \textbf{bots} and \textbf{timezone-aware schedulers}, improving developer productivity and user responsiveness.
  \item Collaborated across product and DevOps teams to deliver stable releases in fast-paced environments.
\end{itemize}

%===================
\section{Projects}

\subsection{LeetCode MCP Server \rside{\href{https://github.com/ayushjaipuriyar/leetcode-mcpserver}{GitHub}, \href{https://www.npmjs.com/package/leetcode-mcpserver}{NPM}}}
\begin{itemize}
  \item Released a modular \textbf{MCP server} exposing problems, contests, solutions, and submission stats; early adoption (~80 downloads) with foundation for growth.
  \item Launched daily challenge, ranking aggregation, and submission reporting tools reducing manual site navigation.
  \item Enabled optional auth for secure submissions and personalized progress.
\end{itemize}

\subsection{Segmentor \rside{\href{https://github.com/ayushjaipuriyar/animepahe-dl}{GitHub}, \href{https://pypi.org/project/animepahe-dl/}{PyPI}}}
\begin{itemize}
  \item Architected cross-platform Python CLI/GUI tool to fetch \texttt{.m3u8} manifests, spawn up to 100 parallel segment downloads, and stitch via \textbf{ffmpeg}; typical 20+ min stream assembled in $\le 60s$ on high bandwidth.
  \item Orchestrated packaging and release (GitHub Actions to PyPI/AUR), enabling rapid distribution and updates.
  \item Introduced segmented retry + checksum validation reducing failed merge artifacts by ~70\% across varied network conditions.
\end{itemize}

\subsection{RIC xApps Malicious Detection \rside{\href{https://github.com/ayushjaipuriyar/ric-xapps-malicious-detection}{GitHub}}}
\begin{itemize}
  \item Engineered cascading multi-class xApps (Near-RT RIC, \textbf{srsRAN}, \textbf{Open5GS}) classifying 10 traffic classes (4 benign, 6 malicious) with sub-second inference.
  \item Generated 15,168 labeled samples (3 emulated UEs) and set up end-to-end orchestration (traffic to RAN lifecycle to logging), saving ~2--3 hrs per run.
  \item Delivered 45\% multi-class accuracy (binary 67--73\%); high F1 on advanced attacks (76\% pulsing UDP flood, 55--63\% others) vs 0--2\%.
\end{itemize}

\subsection{Vantage-14are05 \rside{\href{https://github.com/ayushjaipuriyar/vantage-14are05}{GitHub}}}
\begin{itemize}
  \item Released Linux utility exposing ACPI performance/battery tuning controls for Lenovo laptops.
  \item Added profile switching (performance / balanced / battery-saver) reducing average discharge rate.
  \end{itemize}

%===================
\section{Skills}
\begin{description}
  \item[Languages] C/C++, Java, Python, JavaScript/TypeScript, SQL, Bash, HTML/CSS
  \item[Backend \& Data] Node.js, NestJS, Express, Flask, Django, PostgreSQL, MySQL, MongoDB, Redis, Elasticsearch
  \item[Frontend] React JS, Next.js, Redux, Bootstrap
  \item[ML/Data Tools] Pandas, NumPy, PyTorch, TensorFlow, Scikit-learn, Matplotlib
  \item[DevOps/Cloud] AWS (EC2, S3, CloudFront), GCP, Docker, GitHub Actions, Kubernetes, Cloudflare, CI/CD
  \item[Testing/Tooling] Jest, Postman, Git, npm/Yarn/Pnpm
  \item[Practices] Microservices, REST, WebSockets, GraphQL, Agile/Scrum, OOP, SDLC
\end{description}


% \subsection{Movie Recommendation System \rside{\href{https://github.com/ayushjaipuriyar/movie-recommendation-engine}{GitHub}}}
% \begin{itemize}
%   \item Designed a responsive, mobile-friendly user interface with ReactJS emphasizing UI/UX best practices.
% \end{itemize}
\section{Publications}
%=====================
\begin{enumerate}
  \item [2025] \textbf{A. Jaipuriyar}, A. Yadav, S. Roy, and U. Rawat, “A lossless image encryption technique using chaotic map and DNA encoding,” \textit{Multimedia Tools and Applications}, Apr. 2025. doi: \href{https://doi.org/10.1007/s11042-025-20851-w}{10.1007/s11042-025-20851-w}
\end{enumerate}

\section{Certifications}
%=======================
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
  \item \textbf{Node.js, Express, MongoDB \& More: The Complete Bootcamp 2022\rside{Udemy}}
  \item \textbf{Python Masterclass \rside{Udemy}}
  \item \textbf{AWS Machine Learning Foundations\rside{Udacity}}
  \item \textbf{React - The Complete Guide \rside{Udemy}}
  \item \textbf{DFo Database Foundations Learner \rside{Oracle}}
  \item \textbf{Red Hat System Administration I (RH124 )/ II (RH134) \rside{Red Hat}}
  \item \textbf{C and C++ Specialization \rside{Coursera}}
\end{enumerate}

\end{document}
