%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[margin=0.4in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\titlespacing*{\section}{0pt}{6pt}{10pt}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% ATS FIX: Use plain text for phone (callto: protocol not ATS-parseable)
\begin{center}
  \textbf{\Huge \scshape Ayush Jaipuriyar} \\ \vspace{1pt}
  \small
  +91 9968302859 $|$
  \href{mailto:ayushjaipuriyar21@gmail.com}{\underline{ayushjaipuriyar21@gmail.com}} $|$
  Bangalore, India \\
  \href{https://portfolio.ayushjaipuriyar.uk}{\underline{portfolio.ayushjaipuriyar.uk}} $|$
  \href{https://www.linkedin.com/in/ayushjaipuriyar}{\underline{linkedin.com/in/ayushjaipuriyar}} $|$
  \href{https://github.com/ayushjaipuriyar}{\underline{github.com/ayushjaipuriyar}}
\end{center}

%-----------SUMMARY-----------
% ATS FIX: Expanded summary with high-frequency ATS keywords:
% added "distributed systems", "system design", "cloud-native", "microservices architecture", "Agile"
\section{Professional Summary}
\small{
Full-stack software engineer with 2+ years of experience designing and shipping distributed systems, microservices architectures, and cloud-native web and mobile applications. Proficient in TypeScript, Python, Node.js, NestJS, React, Next.js, React Native, PostgreSQL, MongoDB, Redis, Kafka, Docker, Kubernetes, AWS, Cloudflare, and CI/CD with GitHub Actions. Experienced in system design, API development (REST, GraphQL, WebSockets), performance optimization, and Agile delivery.
}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Glasgow}{Sep. 2024 -- Dec. 2025}
{M.Sc. in Computer Science}{Glasgow, UK}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Full Stack Software Developer}{Feb. 2026 -- Present}
{Seabuddy}{Singapore}
\resumeItemListStart
\resumeItem{Architected a RAG-based AI assistant using Cloudflare AutoRAG, Workers, and Hono, enabling $\sim$300 DAU to query policy documents instantly, cutting average manual lookup time by $\sim$70\%.}
\resumeItem{Engineered a coin-based gamification system (tasks, events, streaks) that grew DAU by $\sim$20\% (from $\sim$250 to $\sim$300 active users) within 60 days of launch.}
\resumeItem{Designed a multi-tenant platform architecture with per-tenant isolated databases and async PDF ingestion pipelines (CF Queues, R2, KV), enabling onboarding of multiple shipping companies with zero cross-tenant data leakage.}
\resumeItem{Optimized backend and database query plans, reducing P50 API latency from 320ms to 140ms (56\% improvement) and improving throughput under peak load.}
\resumeItem{Shipped a React Native app (iOS/Android) with social feed, events, and real-time group chat via WebSockets, serving 1,000+ users with support for 200+ concurrent connections.}
\resumeItemListEnd

\resumeSubheading
{Full Stack Software Engineer}{Jan. 2024 -- Sep. 2024}
{Healthtrip}{Noida, India}
\resumeItemListStart
\resumeItem{Increased API throughput from 120 to 210 RPS by migrating a PHP monolith to NestJS microservices, improving system reliability by 75\%.}
\resumeItem{Engineered REST, GraphQL, and WebSocket APIs serving 8,000+ DAU, reducing P50 response times by 45\% (220ms $\to$ 120ms) through query optimization and connection pooling.}
\resumeItem{Implemented Redis caching layer, reducing database reads by 70\% and cutting read latency from 300ms to 30ms (90\% improvement).}
\resumeItem{Introduced a custom i18n translation system covering 9 languages, driving 75\% engagement growth (5K $\to$ 8.75K DAU) across non-English markets.}
\resumeItem{Spearheaded multilingual Elasticsearch integration, accelerating search throughput from 50 to 80 results/sec (60\% improvement).}
\resumeItem{Engineered a Kafka-based notification pipeline processing 10,000+ events/day, cutting P95 delivery latency by 30\%.}
\resumeItem{Automated CI/CD pipelines using GitHub Actions and Docker across AWS and Cloudflare, reducing deployment cycle from $\sim$2 hours to under 10 minutes ($\sim$90\%) and cutting page load time by 50\% (3.2s $\to$ 1.6s).}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{Jun. 2023 -- Dec. 2023}
{AST Consulting}{New Delhi, India}
\resumeItemListStart
\resumeItem{Launched a GenAI SaaS platform for social media content generation (React, NestJS, MongoDB), onboarding 200+ users within 3 months and supporting 50+ concurrent content generation requests.}
\resumeItem{Engineered REST and GraphQL APIs in NestJS integrating OpenAI GPT models, with retry logic and token-budget management, achieving $<$500ms median response time under production load.}
\resumeItem{Integrated Stripe and Chargebee subscription billing, adopted by 25\% of users within launch quarter, and automated Telegram bot notification workflows.}
\resumeItem{Optimized MongoDB aggregation queries and caching layers, reducing latency from 320ms to 180ms (44\%) for data-heavy analytics dashboards.}
\resumeItem{Provisioned AWS infrastructure with GitHub Actions CI/CD and CloudFront CDN, reducing image load times by 50\%, accelerating deployments by 40\%, and sustaining 95\%+ uptime.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{LeetCode MCP Server} $|$ \emph{Node.js, TypeScript, Anthropic, OpenAI}}{\href{https://github.com/ayushjaipuriyar/leetcode-mcpserver}{GitHub}}
\resumeItemListStart
\resumeItem{Built and published an npm MCP server exposing LeetCode GraphQL endpoints for problems, user profiles, and code submission; implemented submission relay with polling, caching, and rate-limit handling.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{TurboM3U8} $|$ \emph{Python, ffmpeg, tkinter, PyQT}}{\href{https://github.com/ayushjaipuriyar/animepahe-dl}{GitHub}}
\resumeItemListStart
\resumeItem{Built a multi-threaded CLI tool for downloading and assembling HLS .m3u8 streaming segments with robust error handling and recovery logic, improving download reliability by 70\% vs single-threaded baseline.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Near-RT RIC ML-Based Malicious Traffic Detection} $|$ \emph{Python, PyTorch, TensorFlow, O-RAN, ML}}{\href{https://github.com/ayushjaipuriyar/ric-xapps-malicious-detection}{GitHub}}
\resumeItemListStart
\resumeItem{Developed an ML pipeline for real-time O-RAN traffic analysis with live ingestion and monitoring, achieving \textbf{67--73\%} accuracy and up to \textbf{76\%} F1-score on malicious traffic classification.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Lenovo Vantage-Linux: ACPI Tuning Utility} $|$ \emph{Linux, Unix, ACPI, Bash}}{\href{https://github.com/ayushjaipuriyar/vantage-14are05}{GitHub}}
\resumeItemListStart
\resumeItem{Engineered a command-line Linux utility exposing ACPI performance tuning controls, enabling thermal profile switching and improving battery life by \textbf{20--30\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
% ATS FIX: Replaced tabularx table with plain-text list items.
% Tables are a common ATS parsing failure point. This format
% is fully ATS-parseable while maintaining visual alignment.
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt]
  \small{
  \item \textbf{Languages:} TypeScript, JavaScript, Python, Java, SQL, Go, C/C++, Bash, PHP
  \item \textbf{Frontend:} React, Next.js, Redux, React Native, Expo, HTML, CSS, Responsive Design
  \item \textbf{Backend:} Node.js, NestJS, Express, Hono, Django, Flask, REST APIs, GraphQL, WebSockets, Microservices, API Design
  \item \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis, Firebase, Elasticsearch, BigQuery, Query Optimization
  \item \textbf{Cloud \& DevOps:} AWS (EC2, Lambda, S3, CloudFront, RDS), GCP, Cloudflare (Workers, R2, KV, Queues, AutoRAG), Docker, Kubernetes, Terraform, GitHub Actions, Jenkins, CI/CD, IaC
  \item \textbf{Messaging \& Caching:} Kafka, Redis, BullMQ, Cloudflare Queues, Pub/Sub
  \item \textbf{AI/ML:} OpenAI API, Anthropic API, RAG, PyTorch, TensorFlow, LLM Integration, AI/ML Integration
  \item \textbf{Testing:} Jest, PyTest, JUnit, Supertest, Postman, Unit Testing, Integration Testing
  \item \textbf{Tools:} Git, Sequelize, Jira, Linux, Bash, Agile/Scrum, Technical Documentation
  }
\end{itemize}

\end{document}
