\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\setlength{\footskip}{5pt}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
        \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
        \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ayush Jaipuriyar} \\ \vspace{1pt}
    \small 9968302859 $|$ \href{mailto:ayushjaipuriyar21@gmail.com}{\underline{ayushjaipuriyar21@gmail.com}} $|$
    \href{https://linkedin.com/in/ayushjaipuriyar}{\underline{linkedin}} $|$
    \href{https://github.com/ayushjaipiuriyar}{\underline{github}}
\end{center}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
                    \textbf{Languages}{: C/C++, Python, Java, JavaScript, HTML/CSS, SQL} \\
                    \textbf{Frameworks/Libraries}{: React, Node.js, Flask, Material-UI, Expressjs, pandas, NumPy, Matplotlib, Scikit‑learn} \\
                    \textbf{Database}{: MongoDB}
                    \textbf{Developer Tools}{: Git, Docker,Google Cloud Platform} \\
              }}
\end{itemize}

%

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Manipal University Jaipur}{CGPA 8.8}
{B.Tech, Infromation Technology}{Oct. 2020 -- Present}
\resumeSubheading
{Delhi Public School}{Percentage 90\%}
{Class $12^{th}$}{2018 -- 2020}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Summer Intern}{June 2022 -- July 2022}
{Gail Training Institute}{Noida}
\resumeItemListStart
\resumeItem {Obtained an opportunity to work as a full-stack developer and build a new website using the MERN stack.}
\resumeItem {Built the website from the ground up, ensuring simplicity and fast loading times, while also enhancing its security against cyber attacks.}
\resumeItem {Ensuring website functionality and stability across different devices.}
\resumeItem {Implemented a robust and secure backend using Express.js, while utilizing MongoDB as the database technology and React.js for the frontend.}
\resumeItem{Designed a sleek and minimalistic website with an attractive user interface, showcasing a well-integrated combination of these technologies. Successfully reduced the website loading time by 30\% and improved user experience.}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Mentee}{May 2022 -- July 2022}
{Microsoft Engage 2022}{Remote}
\resumeItemListStart
\resumeItem {Built a recommendation system using Python to predict movies that users may be interested in based on their past movie ratings.}
\resumeItem {Obtained the dataset for the project from MovieLens.}
\resumeItem{Programmed an interactive web page using ReactJS to acquire movie ratings from users and exhibit the recommended movies.}
\resumeItem {Utilized Python as the backend programming language with designated endpoints for receiving and transmitting requests for getting recommended movies and submitting movie ratings.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Movie Recommendation System} $|$ \emph{Python, Flask, React, Machine Learning}}{\href{https://github.com/ayushjaipuriyar/movie-recommendation-engine}{\underline{Github}}}
\resumeItemListStart
\resumeItem {Built a recommendation system using Python to predict movies that users may be interested in based on their past movie ratings.}
\resumeItem {Obtained the dataset for the project from MovieLens.}
\resumeItem {Programmed an interactive web page using ReactJS to acquire movie ratings from users and exhibit the recommended movies.}
\resumeItem {Utilized Python as the backend programming language with API using express for receiving and transmitting requests for getting recommended movies and submitting movie ratings.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Vantage-14are05} $|$ \emph{Bash}}
{
    \href{https://github.com/ayushjaipuriyar/vantage-14are05}{\underline{Github}},
    \href{https://aur.archlinux.org/packages/vantage-14are05-git}{\underline{AUR}}
}
\resumeItemListStart
\resumeItem {Created a Bash script utilizing acpi\_calls to modify performance modes and battery charging options on the Lenovo Ideapad Slim 5 AMD laptop, and published it to the Arch User Repository.}
\resumeItemListEnd
\resumeSubHeadingListEnd




%-----------Certifications-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
                    \textbf{Udemy}{: Node.js, Express, MongoDB \& More: The Complete Bootcamp 2022} \\
                    \textbf{Oracle}{: DFo Database Foundations Learner} \\
                    \textbf{RedHat}{: Red Hat System Administration I (RH124 )/II (RH134)} \\
                    \textbf{Coursera}{: C and C++ Specialization (C++ For C Programmers, Part A; C++ For C Programmers, Part B; C for Everyone: Structured Programming; C for Everyone: Programming Fundamentals
                        )}
              }}
\end{itemize}

%-------------------------------------------
\end{document}