%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Full Stack Software Developer}{Feb. 2026 -- Present}
{Seabuddy}{Singapore}
\resumeItemListStart
\resumeItem{Architected a RAG-based AI assistant using Cloudflare AutoRAG, Workers, and Hono, enabling $\sim$300 DAU to query policy documents instantly, cutting average manual lookup time by \textbf{$\sim$70\%}.}
\resumeItem{Engineered a coin-based gamification system (tasks, events, streaks) that grew DAU by \textbf{$\sim$20\%} (from $\sim$250 to $\sim$300 active users) within 60 days of launch.}
\resumeItem{Designed a multi-tenant platform architecture with per-tenant isolated databases and async PDF ingestion pipelines (CF Queues, R2, KV), enabling onboarding of multiple shipping companies with zero cross-tenant data leakage.}
\resumeItem{Optimized backend and database query plans, reducing P50 API latency from 320ms to 140ms (\textbf{56\%} improvement) and improving throughput under peak load.}
\resumeItem{Shipped a React Native app (iOS/Android) with social feed, events, and real-time group chat via WebSockets, serving \textbf{1,000+} users with support for \textbf{200+} concurrent connections.}
\resumeItemListEnd

\resumeSubheading
{Full Stack Software Engineer}{Jan. 2024 -- Sep. 2024}
{Healthtrip}{Noida, India}
\resumeItemListStart
\resumeItem{Increased API throughput from 120 to 210 RPS by migrating a PHP monolith to NestJS microservices, improving system reliability by \textbf{75\%}.}
\resumeItem{Engineered REST, GraphQL, and WebSocket APIs serving \textbf{8,000+} DAU, reducing P50 response times by \textbf{45\%} (220ms $\to$ 120ms) through query optimization and connection pooling.}
\resumeItem{Implemented Redis caching layer, reducing database reads by 70\% and cutting read latency from 300ms to 30ms (\textbf{90\%} improvement).}
\resumeItem{Introduced a custom i18n translation system covering 9 languages, driving 75\% engagement growth (5K $\to$ 8.75K DAU) across non-English markets.}
\resumeItem{Spearheaded multilingual Elasticsearch integration, accelerating search throughput from 50 to 80 results/sec (60\% improvement).}
\resumeItem{Engineered a Kafka-based notification pipeline processing 10,000+ events/day, cutting P95 delivery latency by 30\%.}
\resumeItem{Automated CI/CD pipelines using GitHub Actions and Docker across AWS and Cloudflare, reducing deployment cycle from $\sim$2 hours to under 10 minutes (\textbf{$\sim$90\%}) and cutting page load time by 50\% (3.2s $\to$ 1.6s).}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{Jun. 2023 -- Dec. 2023}
{AST Consulting}{New Delhi, India}
\resumeItemListStart
\resumeItem{Launched a GenAI SaaS platform for social media content generation (React, NestJS, MongoDB), onboarding \textbf{200+} users within 3 months and supporting \textbf{50+} concurrent content generation requests.}
\resumeItem{Engineered REST and GraphQL APIs in NestJS integrating OpenAI GPT models, with retry logic and token-budget management, achieving \textbf{$<$500ms} median response time under production load.}
\resumeItem{Integrated Stripe and Chargebee subscription billing, adopted by 25\% of users within launch quarter, and automated Telegram bot notification workflows.}
\resumeItem{Optimized MongoDB aggregation queries and caching layers, reducing latency from 320ms to 180ms (44\%) for data-heavy analytics dashboards.}
\resumeItem{Provisioned AWS infrastructure with GitHub Actions CI/CD and CloudFront CDN, reducing image load times by 50\%, accelerating deployments by \textbf{40\%}, and sustaining \textbf{95\%+} uptime.}
\resumeItemListEnd

\resumeSubHeadingListEnd
