\documentclass[11pt,letterpaper]{article}

%----------PACKAGES----------
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
%----------PAGE MARGINS----------
% Adjust margins here. Examples:
% \geometry{margin=1in}                         % uniform 1in
% \geometry{margin=0.75in}                      % narrower uniform margins
% \geometry{left=1in,right=1in,top=0.8in,bottom=0.8in} % custom
% \geometry{left=0.75in,right=0.75in,top=0.6in,bottom=0.6in} % typical narrow resume
\geometry{left=0.3in,right=0.3in,top=0.3in,bottom=0in}
%----------DESIGN & TYPOGRAPHY----------
\definecolor{primarycolor}{HTML}{2b2b2b}
\definecolor{linkcolor}{HTML}{2b2b2b}
\definecolor{graytext}{HTML}{555555}
\hypersetup{colorlinks, urlcolor=linkcolor}
\color{primarycolor}
\linespread{0.92}\selectfont
\renewcommand{\arraystretch}{0.92}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\titleformat{\section}{\Large\color{black}\bfseries}{}{0em}{}[\color{gray!50}\titlerule]
\titlespacing*{\section}{0pt}{0pt}{4pt}

%----------CUSTOM COMMANDS----------
\newcommand{\resumeEntry}[5]{%
  \noindent
  \ifstrempty{#1#3}{}{%
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
      {\textbf{\large #1}} & {\textbf{\color{graytext} #3}} \\
    \end{tabular*}
  }%
  \ifstrempty{#2#4}{}{\vspace{-2pt}}%
  \ifstrempty{#2#4}{}{%
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
      {\textit{\normalsize #2}} & {\textit{\color{graytext} #4}} \\
    \end{tabular*}
  }%
  \ifstrempty{#5}{}{
    \begin{itemize}[leftmargin=1.5em, topsep=1pt, itemsep=1pt, parsep=0pt, partopsep=0pt, label=\textbullet]
      #5
    \end{itemize}
  }
  \ifstrempty{#1#2#3#4#5}{}{\vspace{4pt}}
}

\newcommand{\educationEntry}[3]{%
  \noindent
  \makebox[\textwidth]{%
    {\large\textbf{#1} \textbar\ \textit{#2}}%
    \hfill
    {\textbf{#3}}%
  }%
  \par\vspace{2pt}%
}
\newcommand{\CPP}{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}
\newcommand{\certEntry}[3]{%
  \resumeEntry{\ifstrempty{#3}{#1}{\href{#3}{#1}}}{} {#2}{}{}\vspace{-2pt}%
}
\newcommand{\pubEntry}[6]{%
  \noindent
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\textbf{\large \ifstrempty{#5}{#3}{\href{#5}{#3}}}} & {\textbf{\color{graytext} #1}} \\
  \end{tabular*}
  \vspace{-2pt}
  {\textit{#2}} \textemdash{} \textit{#4}\ifstrempty{#6}{}{ \textemdash{} doi: \ifstrempty{#5}{\texttt{#6}}{\href{#5}{\texttt{#6}}}}%
  \vspace{4pt}
}

%----------DOCUMENT START----------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\bfseries Ayush Jaipuriyar} \\[3pt]
    \color{graytext}
    \href{https://www.linkedin.com/in/ayushjaipuriyar}{\faLinkedin\ ayushjaipuriyar}
    \href{mailto:ayushjaipuriyar21@gmail.com}{\faEnvelope\ ayushjaipuriyar21@gmail.com}
    \href{https://github.com/ayushjaipuriyar}{\faGithub\ ayushjaipuriyar}
    \href{tel:+447721170466}{\faPhone\ +44 07721170466} \quad
    \faGlobe\ Glasgow, UK
\end{center}

%-----------EDUCATION-----------
\section{Education}

\educationEntry
{M.Sc. in Computer Science}
{University of Glasgow}
{Sep 2024 -- Sep 2025}

\educationEntry
{B.Tech. in Information Technology}
{Manipal University Jaipur}
{Jun 2020 -- Jun 2024}

%-----------EXPERIENCE-----------
\section{Experience}

\resumeEntry
{Software Developer Intern}
{Healthtrip}
{Noida, India}
{Jan 2024 -- Aug 2024}
{
    \item Migrated 50\% of a \textbf{monolithic backend} to a \textbf{modular architecture}, improving \textbf{scalability and throughput by ~75\%} for 10K+ daily users.
    \item Re-engineered \textbf{multi-lingual content delivery and search pipelines} with \textbf{fuzzy and typo-tolerant queries}, deploying an in-house translation platform, reducing latency by ~90\% and improving search performance by ~60\%.
    \item Developed \textbf{secure production APIs} optimizing interoperability and reducing global page load times by 40–60\%.
    \item Streamlined \textbf{deployment pipelines} with comprehensive testing, cutting deployment time from hours to minutes and accelerating feature delivery by ~30\%.
    \item Collaborated across \textbf{frontend, mobile, and backend teams} to optimize system reliability and development efficiency.
}

\resumeEntry
{Software Developer Intern}
{AST Consulting}
{New Delhi, India}
{Jun 2023 -- Aug 2023}
{
    \item Built and maintained \textbf{backend services} for modular, high-performance operations.
    \item Launched a \textbf{CDN}, cutting image load times by ~50\% and latency by ~40\%.
    \item Implemented \textbf{CI/CD pipelines} and automated deployments, ensuring 95\%+ uptime and 40\% faster releases.
    \item Introduced structured \textbf{code review and version control workflows}, reducing post-release bugs by ~30\%.
    \item Streamlined operations with \textbf{automation bots} and collaborated with cross-functional teams for stable releases.
}

%-----------PROJECTS-----------
\section{Projects}

\resumeEntry
{LeetCode MCP Server}
{}
{\href{https://github.com/ayushjaipuriyar/leetcode-mcpserver}{GitHub} | \href{https://www.npmjs.com/package/leetcode-mcpserver}{NPM}}
{}
{
    \item Developed an \textbf{MCP server} for LeetCode problems, contests, and user data enabling programmatic retrieval and intelligent interaction.
    \item Implemented \textbf{secure code submission, real-time evaluation, and async endpoints} for full workflow automation.
    \item Launched \textbf{daily challenges, ranking aggregation, and submission analytics} for enhanced developer engagement.
}

\resumeEntry
{Segmentor}
{}
{\href{https://github.com/ayushjaipuriyar/animepahe-dl}{GitHub} | \href{https://pypi.org/project/animepahe-dl/}{PyPI}}
{}
{
    \item Python tool to fetch \textbf{.m3u8 manifests}, download 100+ segments in parallel, and assemble streams via \textbf{ffmpeg} in $\leq$60s.
    \item Added \textbf{segmented retries, checksum validation, and error handling}, improving download reliability by ~70\%.
    \item Streamlined \textbf{CI/CD, packaging, and multi-platform distribution} via GitHub Actions, PyPI, and AUR.
}

\resumeEntry
{Near-RT RIC ML-based Malicious Traffic Detection}
{}
{\href{https://github.com/ayushjaipuriyar/ric-xapps-malicious-detection}{GitHub}}
{}
{
    \item Integrated an \textbf{ML pipeline} on \textbf{Near-RT RIC} with multi-class classifiers as cascading xApps interfacing with srsRAN and Open5GS.
    \item Classified 10 traffic classes (4 benign, 6 malicious) using optimized feature extraction and inference.
    \item Achieved high-performance ML metrics: 45\% multi-class accuracy, 67–73\% binary accuracy, and strong F1 scores (up to 76\%).
}

\resumeEntry
{Vantage-14are05}
{}
{\href{https://github.com/ayushjaipuriyar/vantage-14are05}{GitHub}}
{}
{
    \item Released a \textbf{Linux utility} exposing ACPI performance and battery tuning controls for Lenovo laptops.
    \item Added \textbf{profile switching} (performance / balanced / battery-saver) optimizing power consumption.
    \item Reduced average battery discharge rate through automated CPU and system power tuning.
}

%-----------SKILLS-----------
\section{Skills}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}p{0.8\linewidth}}
    \textbf{Languages} & C/C++, Java, Python, JavaScript/TypeScript, SQL, Bash, HTML/CSS \\
    \textbf{Backend} & Node.js, NestJS, Express, Flask, Django, PostgreSQL, MySQL, MongoDB, Redis, Elasticsearch \\
    \textbf{Frontend} & React, Next.js, Redux, Bootstrap \\
    \textbf{ML/Data} & Pandas, NumPy, PyTorch, TensorFlow, Scikit-learn, Matplotlib \\
    \textbf{DevOps/Cloud} & AWS (EC2, S3, CloudFront), GCP, Docker, Kubernetes, GitHub Actions, Cloudflare, CI/CD \\
    \textbf{Testing/Tools} & Jest, Postman, Git, npm/Yarn/Pnpm \\
    \textbf{Practices} & Microservices, REST, WebSockets, GraphQL, Agile/Scrum, OOP, SDLC \\
\end{tabular*}
\vspace{6pt}

%-----------PUBLICATIONS-----------
\section{Publications}
\pubEntry{2025}{Ayush Jaipuriyar, A. Yadav, S. Roy, U. Rawat}{A lossless image encryption technique using chaotic map and DNA encoding}{Multimedia Tools and Applications, Apr. 2025}{https://doi.org/10.1007/s11042-025-20851-w}{10.1007/s11042-025-20851-w}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\certEntry{Node.js, Express, MongoDB \& More: The Complete Bootcamp}{Udemy}{https://ude.my/UC-fd818ef6-3bcc-49cc-a90c-407c5e43b850}
\certEntry{Learn Python Programming Masterclass}{Udemy}{https://www.udemy.com/certificate/UC-b89616fd-a064-4c83-8314-6867d7143ea6/}
\certEntry{AWS Machine Learning Foundations}{Udacity}{https://graduation.udacity.com/confirm/RYJZDCAY}
\certEntry{React - The Complete Guide}{Udemy}{https://www.udemy.com/certificate/UC-53e501f1-5b7f-45d6-acbc-081cff558c41/}
\certEntry{Red Hat System Administration I \& II (RH124/RH134)}{Red Hat}{https://www.redhat.com/en/services/training-and-certification/certification}
\certEntry{C and C++ Specialization (with Honors)}{Coursera}{https://www.coursera.org/account/accomplishments/specialization/certificate/5SLFB6AGNFQR}
\certEntry{JavaScript - The Complete Guide}{Udemy}{https://www.udemy.com/certificate/UC-495bff25-f476-475e-b17d-965581b1933e/}

\end{document}
